\section{Additional derivation and implementation details}
\label{app:details}

\subsection{Proof of Proposition~\ref{prop:law}}

Let $A_g$ be the event that the maximal sampled score equals $z_g$. Since the $N$ candidates are iid,
\[
  \Prob(A_g)=\Prob(\max_i \score_i \leq z_g)-\Prob(\max_i \score_i \leq z_{g-1})
  =F_g^N-F_{g-1}^N.
\]
Conditional on $A_g$, at least one sampled candidate lies in group $g$ and no sampled candidate has a higher score. Uniform tie-breaking selects among the sampled group-$g$ candidates. Because the sampled candidates inside group $g$ are exchangeable and drawn from the conditional distribution $\dist(\cand\mid \score=z_g)$, the selected utility has expectation $\mu_g$. Therefore
\[
  \E[\utility_{\sel(N)}]
  =\sum_g \Prob(A_g)\E[\utility_{\sel(N)}\mid A_g]
  =\sum_g (F_g^N-F_{g-1}^N)\mu_g.
\]
Replacing $\mu_g$ by $z_g$ gives the selected-score identity.

\subsection{Experiment configuration}

The full experiment configuration in \texttt{results/summary.json} is:
\[
\begin{array}{ll}
\text{seed} & 313 \\
\text{offline trajectories} & 450 \\
\text{horizon} & 12 \\
\text{replicates per grid cell} & 64 \\
\text{candidate counts} & 1,2,4,8,16,32,64 \\
\text{model noise scale} & 0.32 \\
\text{safe action} & 0.72 \\
\text{action clip} & 1.65
\end{array}
\]
The support diagnostics are computed from the offline proxy-return distribution. The support boundary used in the microscope is the empirical $q_{95}=6.31391436589062$.

\subsection{Deployment gate}

The deployment gate returns one of four actions: allow candidate sweeps, lower the target return, collect pilot real-utility labels, or block candidate sweeps. In the full run, the in-support and edge-support examples return \texttt{allow\_candidate\_sweep}; the out-of-support example returns \texttt{collect\_pilot\_labels}. This gate is a diagnostic policy for the synthetic environment, not a general deployment standard.

\subsection{Why this is a Decision Transformer audit}

The paper is deliberately not framed as a generic selected-tail warning. The selected object is a return-conditioned action sequence produced by a learned sequence model. The failure is measured against four DT-specific quantities:
\begin{enumerate}
  \item the requested return-to-go prompt,
  \item the empirical return support of the offline dataset,
  \item the proxy return that the model and selector use for prompt satisfaction,
  \item the real utility induced by executing the selected actions.
\end{enumerate}
The same finite-pool accounting could be used in many settings, but the scientific question here is narrower: when does increasing the candidate count for a high return-to-go prompt move a Decision-Transformer-style policy into unsupported action space?

\begin{table}[t]
\centering
\small
\caption{\textbf{Anti-duplication audit.} The paper's evidence object is return-support mismatch, not a generic score-tail wrapper.}
\label{tab:antidup}
\begin{tabularx}{\linewidth}{p{0.24\linewidth}p{0.30\linewidth}X}
\toprule
Axis & generic selected-tail paper & this paper \\
\midrule
Selected object & candidate answer, rollout, or plan & return-conditioned action sequence from a DT-style policy \\
Support variable & often absent or implicit & offline proxy-return quantiles and behavior action likelihood \\
Failure signal & score improves, metric drops & prompt satisfaction improves while support gap, action risk, and real utility expose extrapolation \\
Repair signal & generic reranker or calibration & support-target lowering, behavior likelihood, pilot real-utility labels, and oracle real utility \\
Controls & usually only low versus high $N$ & in-support helps, out-of-support hurts, anti-aligned score hurts, target-overshoot boundary shifts \\
Claim boundary & broad score-tail concern & controlled synthetic offline-RL mechanism, no benchmark-scale claim \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Candidate generation details}

The offline dataset contains behavior trajectories generated by a one-dimensional action process. Actions near the safe region have proxy and real rewards that are nearly aligned. Actions above the safe threshold are underpriced by the proxy reward and punished by the real reward. The learned policy conditions on state, previous action, time, and remaining return-to-go. High return prompts therefore push the learned policy toward larger action magnitudes, especially when sampling noise gives the selector many candidate action sequences to choose from.

For a candidate action sequence $a_{1:T}$, proxy return is
\[
  \score(a_{1:T})=\sum_{t=1}^T \left(a_t-0.025a_t^2\right),
\]
while real utility is
\[
  \utility(a_{1:T})=\sum_{t=1}^T
  \left(a_t-0.025a_t^2
  -10\max(|a_t|-0.72,0)^2
  -0.18\max(a_t-1.20,0)\right).
\]
The real-utility penalty is intentionally convex beyond the behavior-safe region. This creates a clean return-support microscope: proxy return can continue to reward larger actions even after the behavior distribution no longer provides reliable support.

\subsection{Tiny DT-style model specification}

The learned policy is intentionally small, but it is not a hand-coded oracle. It is fit from the offline trajectory batch by ridge regression over per-timestep return-conditioned features. At each timestep it receives the current state, previous action, time index, and remaining return-to-go. It predicts an action mean, then rollouts add Gaussian residual noise and update the remaining return by subtracting realized proxy reward. This is the minimal interface needed for the paper's question: the user specifies a desired return-to-go, the policy samples action sequences conditioned on that request, and the selector chooses among those sequences.

\begin{table}[t]
\centering
\small
\caption{\textbf{Features in the learned DT-style action model.} The model is small by design, but every feature is tied to the return-conditioned sequence interface.}
\label{tab:model-features}
\begin{tabularx}{\linewidth}{p{0.28\linewidth}X}
\toprule
Feature & Role in the controlled audit \\
\midrule
Intercept & Allows a behavior-policy action baseline. \\
State & Carries cumulative one-dimensional dynamics. \\
Previous action & Gives the policy a short autoregressive memory. \\
Return-to-go & Implements the Decision Transformer-style conditioning signal. \\
Return rate & Converts remaining return into a per-step target pressure. \\
Time fraction & Lets early and late actions respond differently to the same remaining return. \\
State by return interaction & Allows target pressure to change with trajectory state. \\
Squared return rate & Allows nonlinear response to ambitious prompts. \\
Previous action by rate & Allows momentum to interact with desired return. \\
\bottomrule
\end{tabularx}
\end{table}

The feature matrix is standardized except for the intercept. Ridge regularization is $10^{-3}$, with no penalty on the intercept. The residual standard deviation is estimated from the fitted offline actions and lower bounded at $0.035$. During rollout, the action is clipped to $[-0.35,1.65]$, proxy and real rewards are both recomputed from the sampled action, and state evolves as previous state plus action plus small Gaussian dynamics noise. The model therefore cannot directly observe real utility during selection; real utility is used only for evaluation, pilot calibration, and the oracle diagnostic.

\subsection{Selection rules as executable pseudocode}

The selectors share a common candidate pool. For a target return $\tau$, candidate count $N$, support estimator $B$, and learned policy $\pi_\theta$, the experiment first samples candidates
\[
  C=\{c_i\}_{i=1}^N,\quad c_i \sim \pi_\theta(\cdot\mid \tau),
\]
then attaches proxy return, real utility, risk, and behavior log-likelihood to each candidate. The selectors differ only in the final choice:

\begin{enumerate}
  \item \textbf{Naive proxy selection:} choose $\arg\max_{c\in C}(\score(c), \ell_B(c))$.
  \item \textbf{Behavior-likelihood filtering:} keep candidates with $\ell_B(c)$ above the offline fifth or tenth percentile; choose the highest proxy candidate among feasible candidates; if none are feasible, subtract a likelihood shortfall penalty from the proxy.
  \item \textbf{Support target calibration:} replace $\tau$ by $\min(\tau, q)$ for $q\in\{q_{90},q_{95}\}$ before sampling; then apply naive selection to the lower target.
  \item \textbf{Pilot-calibrated selection:} draw a small pilot set, fit a ridge linear model from $(1,\score,\text{risk})$ to real utility, force the risk coefficient to be non-positive if needed, and select the candidate with largest predicted real utility.
  \item \textbf{Oracle-real diagnostic:} choose $\arg\max_{c\in C}(\utility(c),\score(c))$. This is never presented as deployable.
\end{enumerate}

This executable definition is why the repair ladder is auditable. The support-calibrated rows are prompt-changing gates. The likelihood and pilot rows are same-target selectors. The oracle row is an upper bound on recoverable real utility already present in the sampled pool. Keeping these categories separate prevents a common overclaim: saying that every repair ``solves'' the high target when some repairs actually refuse or lower it.

\subsection{Artifact-to-claim traceability}

Table~\ref{tab:traceability} maps the major paper claims to generated artifacts. This table is included to make the submission easy to attack: a reviewer can delete or perturb any artifact and the audit should either regenerate it or fail the relevant claim.

\begin{table}[t]
\centering
\small
\caption{\textbf{Traceability from claims to generated artifacts.}}
\label{tab:traceability}
\begin{tabularx}{\linewidth}{p{0.30\linewidth}p{0.31\linewidth}X}
\toprule
Claim & Artifact & Failure mode caught by audit \\
\midrule
Finite-pool accounting matches Monte Carlo & Accounting validation CSV and Figure~\ref{fig:law} & The max absolute real-utility error exceeds the threshold. \\
Out-of-support candidate-count pressure hurts real utility & Original and expanded summary CSVs & Proxy does not rise, real utility does not fall, or risk does not rise. \\
Supported targets are negative controls & Original summary CSV & In-support real utility falls too much under larger $N$. \\
Anti-aligned score behaves as predicted & Anti-aligned control CSV & The anti-aligned selected tail does not reduce real utility. \\
Repairs recover real utility in this environment & Original and expanded repair rows & Pilot, behavior filter, or oracle gaps are too small. \\
Expanded v3 stress passes & Expansion claims JSON & Any high-N, overshoot, pilot, or noise check fails. \\
Final manuscript is complete & Final v3 PDF & The PDF has fewer than $25$ pages. \\
Forbidden overclaims are absent & README, docs, and paper sources & Broad offline-RL or stale-version claims are found. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Why the small model is not a shortcut}

A harsh reviewer might argue that a linear DT-style model makes the result trivial. The paper's claim does not rely on architectural sophistication. It relies on three conditions: a learned return-conditioned sampler, an offline support frontier, and a proxy-real mismatch in the high-action tail. A larger Transformer would add capacity and benchmark relevance, but it would not remove the need for the return-support audit. If anything, stronger models and richer decoders make it more important to know whether high-return prompts are being satisfied inside or outside behavior support.

The controlled model is also useful because it removes a possible confound. If the failure appeared only in a large neural architecture, a reviewer could blame optimization instability, hidden representation collapse, or benchmark noise. Here the model is simple enough that the failure can be traced through action magnitudes, proxy reward, real penalty, behavior likelihood, and support quantiles. The limitation is explicitly acknowledged: this is mechanism evidence, not benchmark dominance evidence.

\subsection{Expanded CSV schema}

The v3 expansion suite writes \path{results/expansion/expanded_summary.csv}, \path{results/expansion/expanded_trials.csv}, \path{results/expansion/claims.json}, and a manifest. The summary file is the main paper-facing artifact. The trial file keeps selected-candidate rows for forensic checks.

\begin{table}[t]
\centering
\small
\caption{\textbf{Main expanded-suite columns.}}
\label{tab:schema}
\begin{tabularx}{\linewidth}{p{0.25\linewidth}p{0.18\linewidth}X}
\toprule
Column & Type & Meaning \\
\midrule
\texttt{family} & categorical & Candidate-count, target-overshoot, repair, pilot-size, or noise stress. \\
\texttt{selector} & categorical & Naive proxy selector, support target reduction, behavior likelihood, pilot calibration, random, or oracle. \\
\texttt{target\_delta\_q95} & numeric & Requested return minus offline $q_{95}$. \\
\texttt{effective\_target} & numeric & Actual prompt after support calibration, if any. \\
\texttt{selected\_proxy} & numeric & Proxy return of the selected trajectory. \\
\texttt{selected\_real} & numeric & Real utility of the selected trajectory. \\
\texttt{selected\_risk} & numeric & Mean squared excess action beyond the safe action threshold. \\
\texttt{behavior\_logp} & numeric & Gaussian behavior-likelihood proxy under the offline action distribution. \\
\texttt{unsafe\_action\_rate} & numeric & Fraction of selected actions above the safe threshold. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Full \texorpdfstring{$N=256$}{N=256} candidate-count table}

Table~\ref{tab:full-tail} gives the full expanded candidate-count tail. The important point is the coupled movement: proxy return improves, real utility falls, risk rises, and behavior likelihood worsens.

\begin{table}[t]
\centering
\small
\caption{\textbf{Full expanded out-of-support candidate-count tail.}}
\label{tab:full-tail}
\begin{tabular}{rrrrrr}
\toprule
$N$ & proxy $\score$ & real $\utility$ & risk & unsafe rate & behavior logp \\
\midrule
1 & 9.283 & 7.888 & 0.0116 & 0.780 & -4.841 \\
2 & 9.351 & 7.791 & 0.0130 & 0.810 & -4.999 \\
4 & 9.384 & 7.574 & 0.0151 & 0.790 & -5.117 \\
8 & 9.410 & 7.593 & 0.0151 & 0.810 & -5.165 \\
16 & 9.433 & 7.439 & 0.0166 & 0.802 & -5.248 \\
32 & 9.439 & 7.491 & 0.0162 & 0.812 & -5.242 \\
64 & 9.469 & 7.353 & 0.0176 & 0.792 & -5.336 \\
128 & 9.483 & 7.380 & 0.0175 & 0.813 & -5.363 \\
256 & 9.507 & 7.258 & 0.0187 & 0.804 & -5.437 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Full target-overshoot table}

Table~\ref{tab:overshoot-full} pairs $N=1$ and $N=256$ for every target gap in the expanded target sweep. The non-monotonic real utility near moderate overshoot is expected: a slightly ambitious prompt can still produce useful larger actions. The collapse appears once the prompt is far outside support and the selector has enough candidates to find high-proxy, high-risk tails.

\begin{table}[t]
\centering
\small
\caption{\textbf{Expanded target-overshoot sweep, $N=1$ and $N=256$.}}
\label{tab:overshoot-full}
\begin{tabular}{rrrrrr}
\toprule
Gap & $N$ & target & proxy $\score$ & real $\utility$ & unsafe rate \\
\midrule
0.00 & 1 & 6.314 & 6.333 & 6.329 & 0.012 \\
0.00 & 256 & 6.314 & 6.514 & 6.456 & 0.063 \\
0.75 & 1 & 7.064 & 7.057 & 6.996 & 0.073 \\
0.75 & 256 & 7.064 & 7.264 & 7.135 & 0.133 \\
1.50 & 1 & 7.814 & 7.806 & 7.680 & 0.258 \\
1.50 & 256 & 7.814 & 8.011 & 7.629 & 0.310 \\
2.25 & 1 & 8.564 & 8.553 & 8.005 & 0.534 \\
2.25 & 256 & 8.564 & 8.756 & 7.718 & 0.560 \\
3.00 & 1 & 9.314 & 9.290 & 7.897 & 0.802 \\
3.00 & 256 & 9.314 & 9.496 & 7.362 & 0.833 \\
3.75 & 1 & 10.064 & 10.037 & 6.810 & 0.942 \\
3.75 & 256 & 10.064 & 10.241 & 5.893 & 0.925 \\
4.50 & 1 & 10.814 & 10.796 & 4.753 & 0.986 \\
4.50 & 256 & 10.814 & 10.984 & 3.578 & 0.984 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Repair interpretation}

The repair ladder contains two qualitatively different interventions. Target-lowering interventions, such as q90 and q95 support calibration, change the effective prompt. They are deployment decisions: ``this prompt is not supported, so lower it.'' Likelihood and pilot calibration interventions keep the high target but change which candidate is selected. They are selection repairs: ``this prompt is risky, so select a candidate whose behavior likelihood or pilot-predicted real utility is credible.''

This distinction matters for reviewer interpretation. It would be misleading to say q90 calibration ``beats'' raw high-target selection, because it is solving a different prompt. It is fair to say it reduces risk and keeps the policy inside the support envelope. It is fair to compare likelihood and pilot selectors directly against raw high-target selection because they operate on the same high-target candidate pool.

\subsection{Repair ladder across \texorpdfstring{$N=64,128,256$}{N=64,128,256}}

\begin{table}[t]
\centering
\small
\caption{\textbf{Repair ladder at high candidate counts.}}
\label{tab:repair-alln}
\begin{tabular}{lrrrr}
\toprule
Selector & $N$ & proxy $\score$ & real $\utility$ & risk \\
\midrule
Naive & 64 & 9.464 & 7.410 & 0.0170 \\
Naive & 128 & 9.482 & 7.421 & 0.0171 \\
Naive & 256 & 9.501 & 7.303 & 0.0183 \\
Behavior q05 & 64 & 9.193 & 8.505 & 0.0058 \\
Behavior q05 & 128 & 9.196 & 8.501 & 0.0059 \\
Behavior q05 & 256 & 9.195 & 8.519 & 0.0056 \\
Pilot-calibrated & 64 & 9.181 & 8.376 & 0.0068 \\
Pilot-calibrated & 128 & 9.177 & 8.435 & 0.0063 \\
Pilot-calibrated & 256 & 9.173 & 8.449 & 0.0060 \\
Oracle real & 64 & 9.226 & 8.501 & 0.0060 \\
Oracle real & 128 & 9.234 & 8.530 & 0.0058 \\
Oracle real & 256 & 9.237 & 8.542 & 0.0058 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Claim thresholds}

The expanded claim JSON records the checks in Table~\ref{tab:claims}. These thresholds are deliberately tied to the paper's claims. If a future edit weakens one of the effects, the claim audit should fail rather than silently preserving old prose.

\begin{table}[t]
\centering
\small
\caption{\textbf{Expanded v3 claim checks.}}
\label{tab:claims}
\begin{tabularx}{\linewidth}{Xrrr}
\toprule
Check & observed & threshold & pass \\
\midrule
Proxy return rises through $N=256$ & 0.224 & $>0.100$ & yes \\
Real utility drops through $N=256$ & -0.629 & $<-0.250$ & yes \\
Selected risk rises through $N=256$ & 0.0071 & $>0.005$ & yes \\
Pilot repair recovers raw tail & 1.146 & $>0.450$ & yes \\
Behavior filter recovers raw tail & 1.216 & $>0.450$ & yes \\
Oracle gap shows recoverable candidates & 1.239 & $>0.600$ & yes \\
High-gap target overshoot worsens at high $N$ & -1.174 & $<-0.200$ & yes \\
Pilot size changes calibrated real utility & 0.443 & $>0.030$ & yes \\
Noise scale changes unsafe-action rate & 0.113 & $>0.020$ & yes \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Expanded design matrix}

The v3 expansion was designed as a set of reviewer attacks rather than a single larger run. Each family asks whether a different explanation can defeat the claim. The candidate-count family attacks the possibility that the $N=64$ result is a shallow artifact. The target-overshoot family attacks the support-boundary story. The repair family attacks whether the failure is recoverable from the same candidate pool. The pilot and noise families attack operational sensitivity.

\begin{table}[t]
\centering
\small
\caption{\textbf{Expanded experiment design matrix.} Every family is generated by the public expansion script and written to the same summary CSV.}
\label{tab:design-matrix}
\begin{tabularx}{\linewidth}{p{0.22\linewidth}p{0.22\linewidth}p{0.20\linewidth}X}
\toprule
Family & Grid & Main stress & Reviewer question \\
\midrule
Candidate count & $N=1$ to $256$ & fixed $q_{95}+3$ target & Does the out-of-support failure survive beyond the original $N=64$ range? \\
Target overshoot & gaps $0$ to $4.5$ & $N=1$ versus $256$ & Is the support boundary actually where prompt satisfaction and real utility separate? \\
Repair ladder & selectors at $N=64,128,256$ & same high target plus support-lowered prompts & Which repairs change the selected tail, and which simply refuse the unsafe prompt? \\
Pilot labels & $4$ to $64$ labels & calibrated selector at $N=256$ & How much direct utility information is needed before calibration becomes stable? \\
Noise stress & scales $0.16$ to $0.64$ & raw high-target selection & Does stochastic decoding expose more unsupported tail mass? \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Statistical precision of the high-candidate tail}

The expanded candidate-count rows use $42$ independent replicates per $N$. Table~\ref{tab:tail-ci} reports standard errors and approximate $95\%$ half-widths for selected real utility. The $N=1$ to $N=256$ real-utility drop is $0.629$, while the approximate half-widths are $0.103$ and $0.182$ respectively. The effect is therefore not a visual impression from a single curve. The uncertainty is largest at high $N$ because top-score selection is deliberately hunting the noisy extreme tail.

\begin{table}[t]
\centering
\small
\caption{\textbf{Precision of the expanded candidate-count stress.} Half-width is $1.96$ times the standard error across replicates.}
\label{tab:tail-ci}
\begin{tabular}{rrrrrr}
\toprule
$N$ & real mean & real SE & $95\%$ half-width & proxy mean & risk mean \\
\midrule
1 & 7.888 & 0.052 & 0.103 & 9.283 & 0.0116 \\
16 & 7.439 & 0.075 & 0.146 & 9.433 & 0.0166 \\
64 & 7.353 & 0.086 & 0.168 & 9.469 & 0.0176 \\
128 & 7.380 & 0.064 & 0.126 & 9.483 & 0.0175 \\
256 & 7.258 & 0.093 & 0.182 & 9.507 & 0.0187 \\
\bottomrule
\end{tabular}
\end{table}

The same table also shows why proxy-only reporting is misleading. Proxy return rises smoothly as $N$ grows. Real utility has a downward trend with non-monotonic local variation, which is exactly what the theory predicts when the selected tail contains heterogeneous real utilities. Larger candidate pools increase pressure toward high proxy values; they do not guarantee monotone movement in real utility.

\subsection{Per-replicate failure slice}

The mean drop in Table~\ref{tab:tail-ci} is backed by a visible bad tail. At $N=256$, the selected-real distribution has a $10$th percentile of $6.551$, median $7.271$, and $90$th percentile $7.914$. Selected risk has a $10$th percentile of $0.0131$, median $0.0185$, and $90$th percentile $0.0247$. Table~\ref{tab:worst-reps} lists the five lowest-real-utility selected trajectories. Each row still has high proxy return, so these are not failed prompt-satisfaction cases; they are high-proxy trajectories whose action risk and behavior likelihood reveal the hidden cost.

\begin{table}[t]
\centering
\small
\caption{\textbf{Worst selected trajectories under naive $N=256$ out-of-support selection.} Rows are individual replicates from \texttt{expanded\_trials.csv}.}
\label{tab:worst-reps}
\begin{tabular}{rrrrrrrr}
\toprule
Rep. & proxy & real & risk & logp & unsafe & mean act. & max act. \\
\midrule
6 & 9.570 & 5.549 & 0.0334 & -5.977 & 0.750 & 0.815 & 1.250 \\
34 & 9.511 & 5.699 & 0.0318 & -5.814 & 0.667 & 0.810 & 1.179 \\
33 & 9.496 & 6.100 & 0.0283 & -5.727 & 0.750 & 0.808 & 1.158 \\
27 & 9.507 & 6.352 & 0.0263 & -5.652 & 0.667 & 0.809 & 1.131 \\
38 & 9.512 & 6.533 & 0.0248 & -5.639 & 0.833 & 0.810 & 1.190 \\
\bottomrule
\end{tabular}
\end{table}

This failure slice is also a useful sanity check on the mechanism. The selector is not choosing obviously nonsensical proxy values. The selected proxy values are tightly concentrated near $9.5$ and the maximum action values remain inside the clipping range. The problem is subtler: the selected sequences use enough near-boundary and beyond-boundary actions to incur real penalties that the proxy does not price correctly.

\subsection{Target-gap derivative table}

Table~\ref{tab:gap-deltas} reports the $N=256$ minus $N=1$ change at each target gap. The first two rows are benign: high candidate count improves both proxy and real utility near the support boundary. The sign turns around once the target is outside support. At gap $4.5$, proxy still improves by $0.188$, while real utility drops by $1.174$, risk rises by $0.0113$, and behavior log-likelihood falls by $0.651$.

\begin{table}[t]
\centering
\small
\caption{\textbf{Change from $N=1$ to $N=256$ across target gaps.} Negative real deltas identify where high candidate count becomes harmful.}
\label{tab:gap-deltas}
\begin{tabular}{rrrrr}
\toprule
Gap above $q_{95}$ & $\Delta$ proxy & $\Delta$ real & $\Delta$ risk & $\Delta$ logp \\
\midrule
0.00 & 0.182 & 0.127 & 0.0005 & -0.281 \\
0.75 & 0.207 & 0.138 & 0.0006 & -0.310 \\
1.50 & 0.205 & -0.051 & 0.0021 & -0.392 \\
2.25 & 0.203 & -0.287 & 0.0041 & -0.469 \\
3.00 & 0.206 & -0.535 & 0.0062 & -0.535 \\
3.75 & 0.204 & -0.917 & 0.0093 & -0.623 \\
4.50 & 0.188 & -1.174 & 0.0113 & -0.651 \\
\bottomrule
\end{tabular}
\end{table}

This table is the strongest compact argument against a duplicate ``best-of-$N$ wrapper'' reading. The object being swept is not a generic sample count alone. It is a return-to-go prompt measured relative to offline return support. The central empirical claim is a boundary claim: candidate-count pressure is useful while the prompt remains behavior-supported, and it becomes dangerous when prompt satisfaction can be achieved through unsupported action tails.

\subsection{Support metrics are not redundant}

The expanded trials record proxy return, real utility, risk, behavior log-likelihood, unsafe-action rate, mean action, and maximum action. These diagnostics are intentionally overlapping but not interchangeable. Table~\ref{tab:corrs} reports per-trial correlations with selected real utility for several high-$N$ slices. In the raw out-of-support tail, selected risk is almost perfectly anti-correlated with real utility, while behavior log-likelihood is strongly positively correlated. The unsafe-action rate is less reliable because many trajectories are already unsafe by a binary threshold; severity matters more than the count alone.

\begin{table}[t]
\centering
\small
\caption{\textbf{Per-trial diagnostic correlations with selected real utility.} Correlations are computed within each high-$N$ slice.}
\label{tab:corrs}
\begin{tabular}{lrrrr}
\toprule
Slice & proxy & risk & logp & unsafe rate \\
\midrule
Naive candidate-count, $N=256$ & -0.129 & -0.999 & 0.927 & 0.562 \\
Target-overshoot, $N=256$ & -0.572 & -0.881 & 0.684 & -0.468 \\
Repair ladder naive, $N=256$ & -0.111 & -0.998 & 0.918 & 0.670 \\
Behavior q05 repair, $N=256$ & 0.102 & -0.567 & -0.009 & 0.536 \\
Pilot-calibrated repair, $N=256$ & 0.442 & -0.865 & -0.173 & 0.681 \\
\bottomrule
\end{tabular}
\end{table}

The repair rows explain why the paper reports multiple diagnostics. Once a behavior-likelihood filter has already truncated the candidate set, log-likelihood no longer explains much residual variation in real utility. Once a pilot model has learned from real labels, proxy return becomes more informative because the selector is no longer naively maximizing proxy alone. A reviewer should therefore read the diagnostics jointly: risk identifies the penalty channel, log-likelihood identifies support, and proxy identifies prompt satisfaction.

\subsection{Repair decomposition at high candidate count}

Table~\ref{tab:repair-deltas} decomposes each $N=256$ repair relative to naive high-target selection. Same-target selection repairs improve real utility while lowering risk and giving up a modest amount of proxy return. Target-lowering rows lower risk even more, but also solve an easier prompt and therefore are not claimed as same-objective improvements. This distinction is important because it prevents the paper from overstating the repair ladder.

\begin{table}[t]
\centering
\small
\caption{\textbf{Repair deltas relative to naive $N=256$ high-target selection.} Positive $\Delta$ real is better; negative $\Delta$ risk is safer.}
\label{tab:repair-deltas}
\begin{tabular}{lrrrr}
\toprule
Selector & $\Delta$ real & $\Delta$ risk & $\Delta$ proxy & $\Delta$ logp \\
\midrule
Random & 0.582 & -0.0066 & -0.214 & 0.567 \\
Naive q90 & -1.608 & -0.0183 & -3.800 & 5.575 \\
Naive q95 & -0.811 & -0.0181 & -2.982 & 4.868 \\
Behavior q10 & 1.209 & -0.0125 & -0.294 & 0.893 \\
Behavior q05 & 1.216 & -0.0127 & -0.306 & 0.918 \\
Pilot calibrated & 1.146 & -0.0123 & -0.328 & 0.943 \\
Oracle real & 1.239 & -0.0125 & -0.264 & 0.840 \\
\bottomrule
\end{tabular}
\end{table}

The random row is a useful negative-control style observation. Random selection from the high-target candidate pool recovers $0.582$ real-utility points relative to naive selection because it avoids the most extreme proxy tail. That does not make random selection a good deployment strategy. It demonstrates that the candidate pool contains better real-utility trajectories and that the failure is caused by the selection rule's preference for proxy-extreme candidates.

\subsection{Pilot-label efficiency}

The pilot-calibrated selector is deliberately presented as a limited-label diagnostic. Table~\ref{tab:pilot-efficiency} reports the real-utility mean, incremental improvement, and standard error as the number of real-utility pilot labels grows. The largest gain is from four to eight labels, and the result stabilizes by $32$ labels. This supports a practical audit recommendation: before using large candidate counts on out-of-support prompts, collect enough direct utility labels to test whether the proxy tail is aligned.

\begin{table}[t]
\centering
\small
\caption{\textbf{Pilot-label efficiency at $N=256$.} Increment is relative to the previous label budget.}
\label{tab:pilot-efficiency}
\begin{tabular}{rrrr}
\toprule
Pilot labels & real utility & increment & real SE \\
\midrule
4 & 8.077 & -- & 0.054 \\
8 & 8.369 & 0.291 & 0.022 \\
16 & 8.453 & 0.084 & 0.019 \\
32 & 8.517 & 0.064 & 0.009 \\
64 & 8.520 & 0.004 & 0.009 \\
\bottomrule
\end{tabular}
\end{table}

The pilot result should not be read as a universal label-budget law. It is a measured property of this controlled environment and feature set. Its role is to show that direct real-utility feedback can identify the bad proxy tail with a small but nonzero budget, and to make the cost of that evidence explicit.

\subsection{Rollout-noise stress as an inference-time attack}

Table~\ref{tab:noise-deltas} reports how the naive $N=256$ minus $N=1$ effect changes with rollout noise. Larger noise increases the selected proxy gain, but it also increases the real-utility loss and risk rise. At noise scale $0.64$, the selector obtains $0.256$ extra proxy return while losing $1.010$ real-utility points. This is an inference-time attack on the paper's own claim: if the failure only appeared at a single decoding noise, it would be much easier to dismiss. Instead, higher stochasticity makes more unsupported tails available.

\begin{table}[t]
\centering
\small
\caption{\textbf{Noise stress deltas from $N=1$ to $N=256$.}}
\label{tab:noise-deltas}
\begin{tabular}{rrrrr}
\toprule
Noise & $\Delta$ proxy & $\Delta$ real & $\Delta$ risk & $\Delta$ unsafe \\
\midrule
0.16 & 0.160 & -0.420 & 0.0048 & 0.012 \\
0.32 & 0.188 & -0.608 & 0.0066 & -0.010 \\
0.48 & 0.219 & -0.782 & 0.0083 & -0.004 \\
0.64 & 0.256 & -1.010 & 0.0105 & 0.010 \\
\bottomrule
\end{tabular}
\end{table}

The unsafe-rate column is intentionally included even though it is not monotone. It reinforces the point from Table~\ref{tab:corrs}: binary threshold counts are a coarse support diagnostic. The risk magnitude and behavior likelihood carry the actual failure signal.

\subsection{RAM-light reproducibility policy}

The expanded suite is intentionally sequential. It does not keep all candidate trajectories from all families in memory at once. Each replicate samples a candidate pool, records only selected-candidate diagnostics and summary statistics, and writes compact CSV and JSON artifacts. Figures are generated from the summary table, not from a retained in-memory trajectory bank. This keeps the v3 expansion compatible with ordinary laptop hardware while still increasing experimental scope.

This matters for the claims. A large but unreproducible run would not make the paper more submission-ready. The acceptance target is instead: enough replicates and stress axes to attack the mechanism, deterministic scripts that regenerate every table, and artifacts small enough for a reviewer or fresh agent to inspect. The repository therefore treats \path{expanded_summary.csv}, \path{expanded_trials.csv}, and \path{claims.json} as audit artifacts rather than temporary notebooks.

\subsection{Additional reviewer attack checklist}

Table~\ref{tab:reviewer-checklist} records the strongest attacks that remain after the v3 expansion and the exact evidence used to answer them. The point is not to claim that every attack is fully solved. The point is to ensure that every paper claim is no broader than the evidence that survives these attacks.

\begin{table}[t]
\centering
\small
\caption{\textbf{Reviewer attack checklist after the v3 expansion.}}
\label{tab:reviewer-checklist}
\begin{tabularx}{\linewidth}{p{0.28\linewidth}p{0.34\linewidth}X}
\toprule
Attack & Evidence in this artifact & Remaining limitation \\
\midrule
The model is too small. & The paper calls it DT-style and focuses on the return-conditioning interface; claims are mechanism-level. & Benchmark-scale Transformers remain future work. \\
The result is synthetic. & Synthetic setup exposes proxy reward, real utility, support boundary, and action risk exactly. & External-control benchmarks are not claimed. \\
The theorem is generic. & The empirical object is target-return overshoot relative to offline support, not only top-score accounting. & The accounting identity is supporting machinery, not the sole novelty. \\
The original $N=64$ result may be accidental. & Candidate-count stress extends to $N=256$ with proxy up, real down, risk up, and logp down. & Larger $N$ values could be explored but are not needed for the stated failure. \\
Candidate selection can help. & In-support and edge-support targets improve under high candidate counts. & The paper makes a conditional boundary claim, not a universal harm claim. \\
Repairs are cherry-picked. & The ladder includes random, target-lowered, likelihood-filtered, pilot-calibrated, and oracle selectors. & Richer support estimators may improve over these simple diagnostics. \\
Pilot calibration is expensive. & Label-size ablation reports gains from $4$ through $64$ labels and shows diminishing returns. & Real deployments may have noisier labels or delayed outcomes. \\
Unsafe rate is confusing. & Correlation analysis shows why risk magnitude and behavior likelihood are more informative. & Better multidimensional support diagnostics are future work. \\
The manuscript duplicates other candidate-count papers. & The evidence centers return-to-go prompts, offline return quantiles, target overshoot, support gates, and pilot real utility. & A future version should add benchmark-scale DT experiments to strengthen distinction further. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Self-attack log}

The following attacks were used to harden the v3 manuscript:
\begin{enumerate}
  \item \textbf{This is only a synthetic environment.} Correct. The paper says this repeatedly and does not claim benchmark-scale offline-RL validity.
  \item \textbf{The finite-pool law is not novel enough.} Correct as a standalone theorem. The law is audit bookkeeping; the contribution is return-support diagnosis for DT prompts.
  \item \textbf{The model is tiny.} Correct. It is a learned DT-style component sufficient for a controlled mechanism study, not a competitive Transformer.
  \item \textbf{Increasing $N$ helps in some settings.} Correct and reported. In-support and edge-support rows help; this is why the paper uses a Tail Phase Diagram rather than a universal harm claim.
  \item \textbf{Support calibration changes the prompt.} Correct. The paper treats it as a deployment gate, not as a same-target optimizer.
  \item \textbf{Pilot calibration needs real labels.} Correct. The label budget ablation makes this cost explicit.
  \item \textbf{The target overshoot result is non-monotonic.} Correct. Moderate overshoot can help; far-out overshoot collapses. This nuance is central.
  \item \textbf{Unsafe-action rate is high even at $N=1$.} Correct. The v3 claim uses selected risk, behavior likelihood, and real utility rather than only unsafe rate.
  \item \textbf{Noise stress could be a decoding artifact.} Correct. That is why it is reported as an inference-time stress, not as a property of all DT decoders.
  \item \textbf{The paper could look like other best-of-$N$ papers.} The manuscript avoids this by foregrounding return prompts, offline support quantiles, behavior likelihood, pilot real labels, and support-target gates.
\end{enumerate}

\subsection{Operational audit protocol}

For a new return-conditioned policy, the audit should proceed as follows:
\begin{enumerate}
  \item Estimate the empirical return support of the offline data, at least $q_{50}$, $q_{80}$, $q_{90}$, $q_{95}$, $q_{99}$, and maximum observed proxy return.
  \item For each target return, record target minus support boundary.
  \item Sample candidate action sequences for several $N$ values, including a small $N$ baseline and a high-$N$ stress point.
  \item Log selected proxy return, real utility, action risk, behavior likelihood, and prompt-satisfaction gap.
  \item Include supported targets where candidate count is allowed to help.
  \item Include out-of-support targets where prompt satisfaction may become misleading.
  \item Compare raw proxy selection against behavior-likelihood filters, target-lowering gates, pilot real-utility calibration, and oracle real utility.
  \item Report where support calibration changes the prompt rather than pretending it solves the same objective.
\end{enumerate}

\subsection{External validity plan}

A stronger future paper should move along four axes. First, replace the one-dimensional synthetic action process with standard offline-control environments while preserving the return-support diagnostics. Second, evaluate larger sequence models and modern DT variants. Third, test whether support-gap and behavior-likelihood diagnostics predict real execution failures under richer dynamics. Fourth, evaluate how many pilot real-utility labels are required before calibration becomes reliable under distribution shift.

The present artifact intentionally covers only the first controlled mechanism layer. Its value is that every number is auditable and every claim is narrow.

\subsection{Final release checklist}

Before release, the repository should satisfy:
\begin{enumerate}
  \item the original full suite regenerates the baseline figures and tables;
  \item the expanded suite regenerates \texttt{results/expansion/claims.json} with \texttt{all\_passed=true};
  \item the final PDF is built at \path{paper/final/best_of_n_decision_transformer-v3.pdf};
  \item the final PDF has at least 25 pages;
  \item the LaTeX log has no undefined references, citation warnings, overfull boxes, fatal errors, or emergency stops;
  \item the claim audit returns \texttt{submission-ready v3};
  \item the Desktop PDF hash matches the repository final PDF hash;
  \item the Desktop source map points this paper to the source folder and GitHub repository.
\end{enumerate}

\subsection{Fresh-agent reproduction manifest}

The final artifact is intended to be inspectable by a fresh agent without private context. A fresh run should begin from the repository root, install the package in the usual local environment if needed, and execute the verification commands in this order:
\begin{enumerate}
  \item \texttt{python -m compileall src tests experiments -q};
  \item \texttt{pytest -q};
  \item \texttt{bash scripts/run\_all.sh};
  \item \texttt{bash scripts/run\_claim\_audit.sh}.
\end{enumerate}
The expected terminal-level outcome is that the test suite passes, the full run reports \texttt{submission-ready v3}, and the claim audit repeats the same verdict. The final PDF should then be rebuilt with the paper build script and checked for page count and LaTeX log cleanliness.

The minimum artifact set for a reviewer or fresh agent is:
\begin{enumerate}
  \item the final PDF in \texttt{paper/final};
  \item the original summary, sweep, repair, anti-aligned, and accounting CSV files in \texttt{results};
  \item the expanded summary, trial, claims, and manifest files in \texttt{results/expansion};
  \item the nine paper figures in \texttt{figures};
  \item the claim-status JSON and markdown files;
  \item the source files for the model, data generator, repair selectors, metrics, and audit.
\end{enumerate}
If any one of these artifacts is missing, the manuscript can still be read, but it is no longer fully submission-auditable. The paper's strongest form is the coupled package: executable experiments, generated evidence, a final manuscript, and a claim audit that can fail unsupported edits.
